---
title: "First check and removal"
output: html_notebook
---
This notebook consists of a first look at the data and elimination of inconsistent, null or non-informative variables.

```{r}
library(tidyverse)
library(tidymodels)

df <- read_csv("data/merged.csv")

df <- df %>%
  mutate(school_id = as_factor(school_id),
         student_id = as_factor(student_id),
         mother_educ = as_factor(mother_educ),
         father_educ = as_factor(father_educ),
         gender = as_factor(gender),
         computer = as_factor(computer),
         internet = as_factor(internet),
         desk = as_factor(desk),
         room = as_factor(room),
         dishwasher = as_factor(dishwasher),
         television = as_factor(television),
         computer_n = as_factor(computer_n), 
         car = as_factor(car),
         book = as_factor(book),
         country_code = as_factor(country_code),
         country_name = as_factor(country_name)
         )
```


An idea could be to use the school identifier as a feature, but it will not be possible because of the high cardinality.
```{r}
n_distinct(df$school_id)
```

ISCED is International Standard Classification of Education.
Parental education seems a priori relevant.

```{r}
df %>%
  count(mother_educ)

df %>%
  count(father_educ)
```
```{r}
df %>%
  count(computer)

df %>%
  count(internet)

df %>%
  count(desk)

df %>%
  count(room)

df %>%
  count(dishwasher)

df %>%
  count(television)

df %>%
  count(computer_n)

df %>%
  count(car)

df %>%
  count(book)

df %>%
  count(year)
```
Dishwasher is totally null, and computer provides less information than computer. Nor can we impute values, since the NAs of computer are the same as those of computer_n. However, we know
that every record is from 2015.

```{r}

df %>%
  select(-computer, -dishwasher, -country_code, -school_id, -student_id, -year) %>%
  write_csv("data/first_removal.csv")

```

